Towards Comparable Active Learning

### 2023-02-16 doc/al_benchmark_paper.tex
upper bound fix
data rework

\subsection{Problem Description}
We assume a dataset $\mathcal{D}$ consisting of a large pool of unlabeled data $\mathcal{U}$ and a small set of labeled data called the seed set $\mathcal{S}$: $\mathcal{D} := (\mathcal{U}, \mathcal{S}); \hspace{2mm} |\mathcal{S}| \ll |\mathcal{U|}$. 
For the purpose of this work, only fully labeled datasets are used and the labels for $\mathcal{U}$ are suppressed until they are selected for labeling.
We consider only classification problems, hence the instances of a dataset have the form $x \in \mathbb{R}^M$ for $\mathcal{U}$ and $(x, y) \in (\mathbb{R}^M, \mathbb{R}^C)$ for $\mathcal{S}$.
To perform classification, a model $\phi_\theta := \mathbb{R}^M \rightarrow \mathbb{R}^C$ is used. To fit the model, it is parameterized by $\theta$ and subjected to loss $l(y, \phi_\theta(x)) := \mathbb{R}^C \times \mathbb{R}^C \rightarrow \mathbb{R}$. For this work, categorical cross-entropy (CE) is used.

@@

>>>>

\subsection{Problem Description}
We assume a dataset $\mathcal{D} := (\mathcal{U}, \mathcal{L})$ consisting of a large pool of unlabeled data $\mathcal{U}$ and a small set of labeled data called the seed set with $|\mathcal{L}| \ll |\mathcal{U|}$. 
For the purpose of this work, only fully labeled datasets are used and the labels for $\mathcal{U}$ are suppressed until they are selected for labeling.
For evaluation purposes we also assume a held-out test set $(x_{test}, y_{test}) \in (\mathbb{R}^M, \mathbb{R}^C)$
We consider only classification problems, hence the instances of a dataset have the form $x \in \mathbb{R}^M$ for $\mathcal{U}$ and $(x, y) \in (\mathbb{R}^M, \mathbb{R}^C)$ for $\mathcal{L}$.
To perform classification, a model $\phi_\theta := \mathbb{R}^M \rightarrow \mathbb{R}^C$ is used. To fit the model, it is parameterized by $\theta$ and subjected to loss $l(y, \phi_\theta(x)) := \mathbb{R}^C \times \mathbb{R}^C \rightarrow \mathbb{R}$. For this work, categorical cross-entropy (CE) is used.
For evaluating classification performance, we use Accuracy \\ [1mm]
Active learning is defined as sequentially selecting single instances of $x_i \in \mathcal{U}$, requesting their label $y_i$ and adding them to the labeled pool $\mathcal{L} := \mathcal{L} \cup (x_i, y_i)$ until a fixed budget $B$ is exhausted $i := 0 \ldots B$.
After each added instance the classification model is retrained according to section \ref{sec:training_the_classifier} and its performance is measured on a held-out test set.
The quality of an active learning algorithm is evaluated by an "anytime" protocol that incorporates classification performance at every iteration, not just the final performance after the budget is exhausted.
We employ normalized AUC:
\begin{equation}
	\operatorname{auc}(\mathcal{U}, \mathcal{L}, \phi, B) := \frac{1}{B} \sum_{i=1}^{B} acc(y_{test}, \phi_i(x_{test}))
\end{equation}
Where $\phi_i$ is the retrained classification model after the i-\textit{th} instance was selected

@@

\subsection{Training the Classifier}\label{sec:training_the_classifier}
\subsection{Evaluation}\label{sec:evaluation}

\section{Ablation Studies}
\begin{itemize}
	\item Weird drop of performance for multiples of batch size (drop\_last in DataLoader)
	\item Reduction of the test set for speed
\end{itemize}
